Hydras \& Co.

### 2023-07-12 doc/chapter-natural-deduction.tex
work on chapter-natural-deduction

>>>>

The following lemma (corresponding to the \texttt{CP} constructor of type \texttt{Prf}) is proven with the help of \texttt{impE}, \texttt{impI}, 
\texttt{sysWeaken} and \texttt{CP}.

\inputsnippets{folLogic/contradiction}

We let the reader consult the proof of the following lemmas, or, much better, re-prove them as exercises.

\inputsnippets{folLogic/nnE}

\inputsnippets{ folLogic/nnI}

\inputsnippets{folLogic/cp1}

\inputsnippets{folLogic/cp2}

\subsection{Rules for derived connectives and quantifiers}

Let us keep in mind that the derived connectives: \texttt{orH}, \texttt{andH}, etc. and the existential quantifier \texttt{existH}  are defined
in terms of \texttt{impH}, \texttt{notH}, \texttt{forallH}.
By unfolding these definitions, we prove easily a few natural deduction rules for the derived symbols. 
For instance, the law of excluded middle for $f$: $ T\sdash \sim f \vee f$
for any $T$,  is just an abbreviation of $T \sdash \sim\sim f \arrow f$.

\inputsnippets{folLogic/noMiddle}

\inputsnippets{folLogic/orI1}

\inputsnippets{folLogic/orI2}
